\bf Faster Neural Machine Translation Inference

### 2018-01-29 fast-beam/fast-beam.tex
fast beam paper

Firstly, the number of classes in many deep-learning applications is small. However, the number of classes in NMT models is typically in the tens or hundreds of thousands, corresponding to the vocabulary size of the output language. For example, ~\cite{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 subword units. This makes the output layer of NMT models very computationally expensive. Figure~\ref{fig:pie-time} shows the breakdown of amount of time during translation our NMT system; nearly 70\% of the time is involved in the output layer. We will look at optimizations which explicitly target the output layer.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{pie-time.png}} 
\end{tabular}
\caption{Time spent during translation (beam size 5)}
\label{fig:pie-time}
\end{figure}

@@

Our training data consisted of the German-English parallel sentences from the Europarl corpus~\citep{Koehn:2005:MTS}. To test inference speed, we used two test sets with differing characteristics:
\begin{enumerate}
   \item \vspace{-2 mm} a subset of the training data, which contains mostly long sentences, and is, of course, in the same domain as the training data
   \item \vspace{-2 mm} a subset of the German-English data from the Open-Subtitles corpus, consisting of mostly short, out-of-domain sentences.
\end{enumerate}
Table~\ref{tab:corpora} gives further details of the test sets.

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		& Subset of training data		& OpenSubtitles \\ \hline
\# sentences  	& 800k 		& 200k \\
\# subwords 	& 5.8m 		& 5.9m \\ 
Avg subwords/sent	& 7.3		& 29.7 \\ \hline
\end{tabular}
\end{center}
\caption{Corpora}
\label{tab:corpora}
\end{table}

@@

>>>>

Firstly, the number of classes in many deep-learning applications is small. However, the number of classes in NMT models is typically in the tens or hundreds of thousands, corresponding to the vocabulary size of the output language. For example, ~\cite{sennrich-haddow-birch:2016:P16-12} experimented with target vocabulary sizes of 60,000 and 90,000 subword units. This makes the output layer of NMT models very computationally expensive. Figure~\ref{fig:pie-time} shows the breakdown of amount of time during translation our NMT system; nearly 70\% of the time is involved in the output layer. We will look at optimizations which explicitly target the output layer.
\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{pie-time.png}} 
\end{tabular}
\caption{Time spent during translation (beam size 5)}
\label{fig:pie-time}
\end{figure}

@@

Our training data consisted of the German-English parallel sentences from the Europarl corpus~\citep{Koehn:2005:MTS}. To test inference speed, we used two test sets with differing characteristics:
\begin{enumerate}
   \item \vspace{-2 mm} a subset of the Europarl training data, which contains mostly long sentences, and is, of course, in the same domain as the training data
   \item \vspace{-2 mm} a subset of the German-English data from the Open-Subtitles corpus, consisting of mostly short, out-of-domain sentences.
\end{enumerate}
Table~\ref{tab:corpora} gives further details of the test sets.

\begin{table}
\begin{center}
\small
\begin{tabular}{|l|r|r|} \hline
		  & Europarl		& OpenSubtitles \\ \hline
\# sentences  	  & 30,000 		& 50,000 \\
\# subwords 	  & 787,908 		& 467,654 \\ 
Avg subwords/sent & 26.3		& 9.4 \\ \hline
\end{tabular}
\end{center}
\caption{Test sets}
\label{tab:corpora}
\end{table}

@@

Fusing the softmax and beam search increase the speed of the output layer by 43\% for beam size 1, decreasing to 25\% for a beam of 10 when translating the Europarl dataset. This led to an overall increase in translation speed of up to 23\%, Figure~\ref{fig:europarl-beam}.

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{europarl-beam.png}} 
\end{tabular}
\caption{Translation speed for Europarl dataset}
\label{fig:europarl-beam}
\end{figure}
